Hydras \& Co.

### 2022-04-13 doc/gaia-chapter.tex
additions to gaia chapter; remove several proof-based definitions

\subsubsection{E0 as an ordinal notation}
The module \href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge} defines an instance of class \texttt{ON E0lt compare}
(see Chapter~\ref{chap:ON}).

\inputsnippets{T1Bridge/T1compareDef}
\inputsnippets{ T1Bridge/T1compareCorrect}
\inputsnippets{T1Bridge/E0compare}
\inputsnippets{T1Bridge/E0Sto}
\inputsnippets{T1Bridge/gEpsilon0}

\inputsnippets{T1Bridge/ExampleComp}

@@

From~\href{../theories/html/gaia_hydras.GF_alpha.html}%
{\texttt{gaia\_hydras.GF\_alpha}}.

@@

>>>>

\subsubsection{E0 as an ordinal notation}

The notion of ordinal notation is defined in Chapter~\ref{chap:ON}. In \href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, we define an instance of class \texttt{ON E0lt compare}.

First, we define an instance of (\texttt{Compare T1}):

\inputsnippets{T1Bridge/T1compareDef}
\inputsnippets{ T1Bridge/T1compareCorrect}

Then, we build an instance of (\texttt{ON E0lt compare}).

\inputsnippets{T1Bridge/E0compare}
\inputsnippets{T1Bridge/E0Sto}
\inputsnippets{T1Bridge/compEpsilon0}
\inputsnippets{T1Bridge/ExampleComp}
\inputsnippets{T1Bridge/gEpsilon0}

@@

\vspace{4pt}

\noindent
From~\href{../theories/html/gaia_hydras.GF_alpha.html}%
{\texttt{gaia\_hydras.GF\_alpha}}.

@@

\subsection{The \texorpdfstring{$L_\alpha$}{\texttt{L\_alpha}} hierarchy (Library \texttt{GL\_alpha})}

The functions $L_\alpha$, described in Sect.~\vref{sect:lalpha-section}  allow us to ``compute'' the length of standard hydra battles. In the same way as for the hierarchies $F_\alpha$ and $H'_\alpha$, we import  definitions and lemmas from the module
~\href{../theories/html/hydras.Epsilon0.L_alpha.html}{Epsilon0.L\_alpha}.

\vspace{4pt}
\noindent
From\href{../theories/html/gaia_hydras.GF_alpha.html}%
{\texttt{gaia\_hydras.GF\_alpha}}.

\inputsnippets{GL_alpha/Ldef}
\inputsnippets{GL_alpha/Leq2}
\inputsnippets{GL_alpha/Leq3}
\inputsnippets{GL_alpha/Leq4}

The following theorem compares the $L_\alpha$ and $H'_\alpha$ hierarchies.

\inputsnippets{GL_alpha/HprimeLAlpha}
